Longer term All-Cause and Cardiovascular Mortality with Intensive Blood Pressure Control: A Secondary Analysis of SPRINT

### 2022-01-07 doc/manuscript.Rmd
bcj edits to Results

@@

tar_load(names = c(recoders,
                   base_viz_inc,
                   base_viz_eff,
                   long_viz_mort,
                   long_viz_cvd,
                   base_ds, 
                   long_ds,
                   long_inf,
                   base_inf,
                   ndi_baseline))

@@

__EHR Ancillary Study__: We examined the trajectory of systolic blood pressure (SBP) following the conclusion of the trial using outpatient SBPs extracted from the electronic health record (EHR). Methods for the linkage of participants to their medical record number and the extraction of vital sign data have been previously described [@drawz_concordance_2020]. Because encounter type information was inconsistently available (i.e. outpatient, inpatient, observation, etc.), we defined a BP measurement as outpatient if there were was not a BP measurement on the preceding or following day, and if there were 2 or less BP measurements on a particular day. We averaged outpatient EHR BP readings when there were 2 on the same day.

@@

@@

The estimated mean SBP among participants randomized to intensive treatment was <placeholder (95% CI)> at 5 years and <placeholder (95% CI)> at 10 years post-randomization (__Figure 3__). For participants randomized to standard treatment, mean SBP was estimated to be <placeholder (95% CI)> at 5 years and <placeholder (95% CI)> at 10 years post-randomization.

@@

tar_load(tbl_characteristics)

@@

tar_load(bp_viz)

>>>>

NOTE: ADD Steve Rapp AS A CO-AUTHOR

@@

tar_load(names = c(recoders,
                   base_viz_inc,
                   base_viz_eff,
                   long_viz_mort,
                   long_viz_cvd,
                   bp_viz,
                   tbl_characteristics,
                   base_ds, 
                   long_ds,
                   long_inf,
                   base_inf,
                   ndi_baseline))

@@

__EHR Ancillary Study__: We examined the trajectory of SBP following the conclusion of the trial using outpatient SBPs extracted from the EHR. Methods for the linkage of participants to their medical record number and the extraction of vital sign data have been previously described [@drawz_concordance_2020]. Because encounter type information was inconsistently available (i.e. outpatient, inpatient, observation, etc.), we defined a BP measurement as outpatient if there were was not a BP measurement on the preceding or following day, and if there were 2 or less BP measurements on a particular day. We averaged outpatient EHR BP readings when there were 2 on the same day.

@@

__ADD 1-2 SENTENCES ON CHARACTERISTICS__ (__Table 1__). Among participants included and not included in the ancillary EHR study, there was no evidence of a difference in study characteristics between participants randomized to intensive versus standard treatment (__eTable 1__).

@@

bp_viz_5yr <- bp_viz |> 
  getElement('levels') |> 
  getElement('data') |> 
  filter(time_months == 60)

bp_viz_5yr <- split(bp_viz_5yr, bp_viz_5yr$group)

bp_viz_10yr <- bp_viz |> 
  getElement('levels') |> 
  getElement('data') |> 
  filter(time_months == '120')

bp_viz_10yr <- split(bp_viz_10yr, bp_viz_10yr$group)

# a temporary function for inline reporting below.
f <- function(d) with(d, .("{Estimate} ({Lower}, {Upper})"))

bp_diff_5yr <- bp_viz |> 
  getElement('diff') |> 
  getElement('data') |> 
  filter(time_months == 60)

t_atten <- bp_viz |> 
  getElement('diff') |> 
  getElement('data') |> 
  filter(find_signchange_lgl(Lower)) |> 
  pull(time_months) |> 
  divide_by(12)

The estimated mean (95% CI) SBP among participants randomized to intensive treatment was `r f(bp_viz_5yr$Intensive)` at 5 years and `r f(bp_viz_10yr$Intensive)` at 10 years post-randomization (__Figure 3__; panel A). For participants randomized to standard treatment, mean (95% CI) SBP was estimated to be `r f(bp_viz_5yr$Standard)` at 5 years and `r f(bp_viz_10yr$Standard)` post-randomization. The difference in mean SBP levels between participants randomized to intensive versus standard treatment, in mm Hg, was `r f(bp_diff_5yr)` at 5 years post-randomization, and was attenuated by `r t_atten` years post-randomization (__Figure 3__; Panel B).

@@

@@
